The Need to Develop a Holistic Infectious Disease Surveillance System

### 2024-09-28 manuscript/manuscript.qmd
Update lineplot code to work with other outcomes and create tables and plots in the manuscript
Use separate files that are run with each manuscript rendering to ensure
correct versions are included

@@

```{=typst}
#let optimal_thresholds = csv("optimal-thresholds.csv")

@@

```{=typst}
#let optimal_thresholds = csv("optimal-thresholds-accuracy.csv")

@@

```{julia}
#| fig-cap: "The accuracy of outbreak detection systems under different testing rates and noise structures. The shaded bands illustrate the 80% central interval, and the solid/dashed lines represent the mean estimate."
#| label: fig-accuracy
include("line-plot.jl")
```

>>>>

```{julia}
#| echo: false
include("optimal-thresholds.jl");
```

@@

```{=typst}
#let optimal_thresholds = csv("thresholds.csv")

#table(
  columns: 10,
  fill: (x, y) => {
    if y == 0 {gray}
    if y == 1 {gray}
  },
  align: center,
  [], table.cell(colspan: 2, align: center, "Test Characteristic"), table.cell(colspan: 7, align: center, "Testing Rate"),
  ..optimal_thresholds.flatten()
)
```

@@

```{=typst}
#let accuracy = csv("optimal-thresholds_accuracy.csv")

#table(
  columns: 10,
    fill: (x, y) => {
      if y == 0 {gray}
      if y == 1 {gray}
    },
  [], table.cell(colspan: 2, align: center, "Test Characteristic"), table.cell(colspan: 7, align: center, "Testing Rate"),
  ..accuracy.flatten()
)
```

The outbreak detection accuracy for each testing scenario, at the optimal thresholds.

@@

```{julia}
#| echo: false
include("line-plot.jl");
```

```{julia}
#| fig-cap: "The accuracy of outbreak detection systems under different testing rates and noise structures. The shaded bands illustrate the 80% central interval, and the solid/dashed lines represent the mean estimate."
#| label: fig-accuracy
accuracy_line_plot
```

```{julia}
#| fig-cap: "The number of unavoidable cases of outbreak detection systems under different testing rates and noise structures. The shaded bands illustrate the 80% central interval, and the solid/dashed lines represent the mean estimate."
#| label: fig-unavoidable
unavoidable_line_plot
```

```{julia}
#| fig-cap: "The detection delay of outbreak detection systems under different testing rates and noise structures. The shaded bands illustrate the 80% central interval, and the solid/dashed lines represent the mean estimate."
#| label: fig-delay
delay_line_plot
```
